---
title: "Religious Stigma OverTime "
author: "Mara Zanin"
description: "PS270 final project"
output:
  distill::distill_article:
    self_contained: false
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

# Religious Stigma Over Time

## Introduction
Has religion become less stigmatized in the last two decades? In this study, I plan to examine the extent to which religious people have endured government restrictions and social hostilities between 2007-2022.

I hypothesize that both of these factors have increased within the set time frame, thus reflecting increased stigmatization. Because of the perceived rise of conservatism in the recent years, highlighting a surge in ideological, polarized conservatism from 2008 onward, I expect that number of government restrictions on religion and social hostilities against religious people will increase over the 16 years. Hopefully, this research of "if" and "how" can lend itself to further study of "why" and conversations about what course of action can reduce religious stigma in the future.


## Data
My data is comprised from 198 countries and territories, which contain more than 99.5% of the world's population, from 2007-2022. My unit of analysis will be all of these territories, over the 16-year span. The null hypothesis is that the passing of time has had no effect on religious stigma levels.

Columns represent various subcategories of two classifications: either government restrictions or social hostilities.
The Government Restrictions Index (GRI) is based on 20 indicators of method that national and local governments use to restrict religions, ranging from 0.0 to 10.0--lowest to highest level of government restrictions. Examples of these subcategories are whether the law provides for "freedom of religion" or whether government interferes with religious practices. Similarly, the Social Hostilities Index (SHI) will be based on 13 indicators of ways that private individuals and social groups infringe upon religious beliefs, ranging from 0.0 to 10.0--lowest to highest level of social hostilities. Examples of these subcategories are instances of hostility over religious conversions or whether women were harassed for violating religious dress codes.
These indexes are calculated based on the comprising parts of each one, to find a total score for each of the selected countries, per year.

I will be creating my own index: Religious Stigma Average (RSA). RSA will be calculated by taking the average of the Government Restrictions Index (GRI) and Social Hostilities Index (SHI) to create a cumulative score for each country, over each year, on a scale from 0.0-10.0--lowest to highest religious stigma. In the final examination, the RSA will be calculated to find an average for all countries/territories, per year.


If I observe that the RSA increases across the units over the span from 2007-2022, I will thus be able to conclude that religion has become more stigmatized in the last two decades. If, on the other hand, the average of these indexes decrease over the allotted time, I will conclude that religion has not become more stigmatized in the last two decades. Finally, if the RSA varies greatly over the 16 years, showing no real pattern, and presenting a p-value of more than the predetermined alpha level of 0.05, I will conclude there is not sufficient evidence to reject the null hypothesis.
If the p-value is less than the predetermined alpha level of 0.05, I will be able to conclude that the result is statistically significant and reject the null hypothesis.


```{r}
library(tidyverse)
religion_data <- readr::read_csv("~/Downloads/Global-Restrictions-on-Religion-2007-2022-Dataset/PublicDataset_ReligiousRestrictions_2007to2022.csv")
```

```{r}
religion_instances <- religion_data |>
group_by(Ctry_EditorialName, Question_Year) |>
  summarize(religion_avg = mean((SHI + GRI)/2, na.rm = TRUE)) 

religion_instance_plot <- religion_instances |>
  ggplot(aes(x = religion_avg)) +
  geom_histogram(col = "lightblue") +
  labs(x = "Religious Stigma Average (RSA)", y = "Number of Instances", title = "Religious Stigma Average (RSA)", subtitle = "Outcome Variable")
religion_instance_plot
```

## Results
```{r}

religion_means <- religion_data |>
  group_by(Ctry_EditorialName, Question_Year) |>
  summarize(religion_avg = mean((SHI + GRI)/2, na.rm = TRUE)) |>
  group_by(Question_Year) |>
  summarize(country_avg = mean(religion_avg, na.rm = TRUE))

religion_SHI_GRI <- religion_means |>
  ggplot(aes(x = Question_Year, y = country_avg)) +
  labs(title = "Religion Stigmatization Over Time", x = "Year (2007-2022)", y = "Religious Stigma Average (RSA)", subtitle = "Averaged from All Countries") +
  geom_point() +
  geom_smooth()

religion_SHI_GRI
```



```{r}
library(broom)
library(knitr)
fit <- lm(country_avg ~ Question_Year, data = religion_means)

fit |>
  tidy() |>
  kable(digits = 3, 
    caption = "Linear Regression: Religious Stigma Trends",
    col.names = c("Term", "Estimate", "Std. Error", "t-statistic", "p-value"))
```


Results section: interpretation of the main coefficient of interest and describing if it is statistically significant

Results section: substantive meaning of relationship and if we should interpret it causally



## Conclusion

Has religion become less stigmatized in the last two decades? Based on this data, as displayed in the graph, the answer is no. The visualization shows a low Religious Stigma Average (RSA) score across countries, starting at around 2.20 in 2007 and growing exponentially until 2012, reaching a high of just over 3.0. After that, the score dips dramatically to about 2.4 in 2014, and then follows with a small increase, decrease, and then plateau over the following 6 years, staying between 2.75 and 3.0.

There are a few reasons for the significant changes in religious stigma over this allotted time period. The initial, large but gradual increase in RSA is commonly associated with rising anti-Muslim sentiments, sectarian violence in Nigeria, and increased harassment regarding religious dress for women. The steep increase in 2012 is generally associated with the Arab Spring, occurring just before in 2010-2011. The relatively stabilized scores from 2016 on remain high, and typically connected with the decline of religious affiliation as a whole. Responding to the original question, beyond the smaller trends within, the graph shows an increase in RSA over time, as displayed by the mean line.
The regression shows a Question_Year value of about 0.03, which means for every one-year increase, the average Religious Stigma Average increases by 0.03. This is neither a huge or a catastrophic increase, but it is not negligible. This means within about 33 years, religious stigma average increases 10%.

With only short decreases, there is long-term exponential growth in religious stigma, showing that religious stigma has not decreased over time, rather it has grown.

