---
title: "Religious Stigma Over Time "
author: "Mara Zanin"
description: "PS270 final project"
output:
  distill::distill_article:
    self_contained: false
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

## Introduction
Has religion become less stigmatized in the last two decades? In this study, I plan to examine the extent to which religious people have endured government restrictions and social hostilities between 2007-2022, based on Pew Research Center's calculations (Pew, 2025).

I hypothesize that both of these factors have increased within the set time frame, thus reflecting increased stigmatization. Because of the perceived rise of conservatism in the recent years, highlighted by a surge in ideological conservatism and polarization from 2008 onward, I expect that number of government restrictions on religion and social hostilities against religious people will increase over the 16 years. Hopefully, this research of "if" and "how" can lend itself to further study of "why," and conversations about what course of action can reduce religious stigma in the future.


## Data
My data is comprised from 198 countries and territories, which contains more than 99.5% of the world's population from 2007-2022. My unit of analysis will be all of these territories, over the 16-year span. The null hypothesis is that the passing of time has had no effect on religious stigma levels.

Columns in the original dataset represent various subcategories of two classifications: government restrictions or social hostilities.
The Government Restrictions Index (GRI) is based on 20 indicators of methods that national and local governments used to restrict religions, ranging from 0.0 to 10.0--lowest to highest level of government restrictions. Examples of these subcategories are whether the law provides for "freedom of religion" or whether government interferes with religious practices. Similarly, the Social Hostilities Index (SHI) is based on 13 indicators of ways that private individuals and social groups infringe upon religious beliefs, ranging from 0.0 to 10.0--lowest to highest level of social hostilities. Examples of these subcategories are instances of hostility over religious conversions or whether women were harassed for violating religious dress codes (Pew, 2025).
These indexes are calculated based on the comprising parts of each one, to find a total score for each of the selected countries, per year.

I have also created my own index: The Religious Stigma Average (RSA). RSA will be calculated by taking the average of the Government Restrictions Index (GRI) and Social Hostilities Index (SHI) to create a cumulative score for each country, over each year, on a scale from 0.0-10.0--lowest to highest religious stigma. In the final examination, the RSA will be calculated to find an average for all countries/territories per year, in a longitudinal design study.


If I observe that the RSA increases across the sample over the span from 2007-2022, I will thus be able to conclude that religion has become more stigmatized in the last two decades. If, on the other hand, the average of these indexes decrease over the allotted time, I will conclude that religion has become less stigmatized in the last two decades. Finally, if the RSA varies over the 16 years, shows no real pattern, and presents a p-value of more than a predetermined alpha level of 0.05, I will conclude there is not sufficient evidence to reject the null hypothesis.
If the p-value is less than the predetermined alpha level of 0.05, and there is an observable positive or negative relationship between RSA and years, I will be able to conclude that the result is statistically significant and reject the null hypothesis.


```{r}
library(tidyverse)
religion_data <- readr::read_csv("~/Downloads/Global-Restrictions-on-Religion-2007-2022-Dataset/PublicDataset_ReligiousRestrictions_2007to2022.csv")
```

```{r}
religion_instances <- religion_data |>
group_by(Ctry_EditorialName, Question_Year) |>
  summarize(religion_avg = mean((SHI + GRI)/2, na.rm = TRUE)) 

religion_instance_plot <- religion_instances |>
  ggplot(aes(x = religion_avg)) +
  geom_histogram(col = "lightblue") +
  labs(x = "Religious Stigma Average (RSA)", y = "Number of Instances", title = "Religious Stigma Average (RSA)", subtitle = "Outcome Variable")
religion_instance_plot
```

## Results
```{r}
religion_means <- religion_data |>
  group_by(Ctry_EditorialName, Question_Year) |>
  summarize(religion_avg = mean((SHI + GRI)/2, na.rm = TRUE)) |>
  group_by(Question_Year) |>
  summarize(country_avg = mean(religion_avg, na.rm = TRUE))

religion_SHI_GRI <- religion_means |>
  ggplot(aes(x = Question_Year, y = country_avg)) +
  labs(title = "Religion Stigmatization Over Time", x = "Year (2007-2022)", y = "Religious Stigma Average (RSA)", subtitle = "Averaged from All Countries") +
  geom_point() +
  geom_smooth()

religion_SHI_GRI
```



```{r}
library(broom)
library(knitr)
fit <- lm(country_avg ~ Question_Year, data = religion_means)

fit |>
  tidy() |>
  kable(digits = 3, 
    caption = "Linear Regression: Religious Stigma Trends",
    col.names = c("Term", "Estimate", "Std. Error", "t-statistic", "p-value"))
```

The second visualization shows a lower Religious Stigma Average (RSA) score across countries, starting at around 2.20 in 2007 and growing exponentially until 2012, reaching a high of just over 3.0. After that, the score dips dramatically to about 2.4 in 2014, and then follows with a small increase, decrease, and then plateau over the following 6 years, staying between 2.75 and 3.0. Overall, there was over a 0.5 RSA increase in the allotted time.

The regression shows an estimated coefficient value of about 0.033, which means for every one-year increase, holding all other variables constant, the average Religious Stigma Average increases by 0.033. This is not a relatively huge increase, but it is not negligible. This means within about 33 years, religious stigma average increases 10%. This is significant because it supports the hypothesis that religious stigma has grown over time.
Further, the p-value is 0.005, which is much smaller than the predetermined alpha of 0.05. This indicates there is less than a 5% probability that the observed data occurred by chance. This too supports the hypothesis that religious stigma has grown over time. 
Although this result is statistically significant, we should not jump to interpret it causally. This is because the passage of time is hard to isolate on its own, and there are many things that could cause increasing religious stigma; it cannot be said that the simple passing of time causes it. So, while the two are definitely correlated, we would need to conduct more research to isolate the variables.



## Conclusion

Has religion become less stigmatized in the last two decades? Based on this data, as displayed in the graph, the answer is no. 

There are a few possible reasons for the significant changes in religious stigma over this allotted time period. The initial, large but gradual increase in RSA is commonly associated with rising anti-Muslim sentiments, sectarian violence in Nigeria, and increased harassment regarding religious dress for women. The steep increase in 2012 is generally associated with the Arab Spring, occurring just before in 2010-2011. The relatively stabilized scores from 2016 on remain high, and are typically connected with the decline of religious affiliation as a whole. Responding to the original question, beyond the smaller trends within, the graph shows an increase in RSA over time, as displayed by GRI and SHI averages observably growing, also shown by the mean line. Due to this and the p-value below 0.05, we have sufficient evidence to reject the null hyothesis.

As with any study, there are limitations of the analysis and threats to inference. For one, it's possible that because human rights monitoring has increased, the resulting growing rates of religious stigma could be related to the fact researchers are reporting it more now, not that stigma is rising at the exact patterns displayed.
There are also a few possible confounders. The change in time has resulted in a rise of secularization, a rise that could have an impact in either direction of religious stigma. Time also has come with changing social norms, which could also be impacting stigma average. Although there is not something (for the purposes of this research) that can make time continue progressing forward, these aspects are both impacted by the progression of time and impact religious attitudes, and thus can be considered confounders.

The other limiting aspects is that this data primarily looks at a macro level, assessing whole territories on their largest religious aspects. This presents the possibility that lots of micro-interactions and interpersonal interactions, those not convicted or reported may not be recorded. With more resources, perhaps future researchers would be able to interview more people in the countries and get a sense for the religious stigma present in personal, more hidden culture.

Overall, although this is not where the research on religious injustices should end, this data and analysis provides strong evidence that religious stigma has grown over the last two decades. With this information, we can pursue further, deeper research, and start looking for solutions to lower stigma across the world.

## Citations

Pew Research Center. 2025. “Dataset: Global Restrictions on Religion 2007-2022.” doi: 10.58094/tecg-6392.
