---
title: "PS270 Final Project"
author: "Mara Zanin"
description: "My final project"
output:
  distill::distill_article:
    self_contained: false
---

# Religious Stigma Over Time

## Project thoughts
Has religion become less stigmatized in the last two decades? In this study, I plan to examine the extent to which religious people have endured government restrictions and social hostilities between 2007-2022. I hypothesize that both of these factors have increased within the set time frame, thus reflecting increased stigmatization. Because of the perceived rise of conservatism in the recent years, highlighting a surge in ideological, polarized conservatism from 2008 onward, I expect that number of government restrictions on religion and social hostilities against religious people will increase over the 16 years. My sample is comprised of data from every country, organized first by which country and then by year. After defining information, columns represent subcategories in both government restrictions and social hostilities. My unit of analysis will be 30 randomly selected countries to examine, throughout all 16 years. The Government Restrictions Index (GRI) will be based on 20 indicators of ways that national and local governments restrict religions, ranging from 0.0 to 10.0--from lowest to highest level of government restrictions. Examples of these subcategories are whether the law provides for "freedom of religion" or whether government interferes with religious practices. Similarly, the Social Hostilities Index (SHI) will be based on 13 indicators of ways that private individuals and social groups infringe upon religious beliefs, ranging from 0.0 to 10.0--from lowest to highest level of social hostilities. Examples of these subcategories are whether there were instances of hostility over conversions of religion or whether women were harassed for violating religous dress codes. I will calculate these indexes based on the comprising parts of each one, to find a total score for each of the selected countries. If I observe that the average of these indexes increase across the units over the span from 2007-2022, I will thus be able to conclude that religion has become more stigmatized in the last two decades. If, on the other hand, the average of these indexes decrease over the allotted time, I will conclude that religion has become less stigmatized in the last two decades. Finally, if results vary significantly, remain relatively the same, or show no real pattern, I will conclude that religion has not had a specific trend of becoming more or less stigmatized.


```{r}
library(tidyverse)
religion_data <- readr::read_csv("~/Downloads/Global-Restrictions-on-Religion-2007-2022-Dataset/PublicDataset_ReligiousRestrictions_2007to2022.csv")
head(religion_data)
#religion_data
```
## Table
```{r}

religion_means <- religion_data |>
  group_by(Ctry_EditorialName, Question_Year) |>
  summarize(religion_avg = mean((SHI + GRI)/2, na.rm = TRUE)) |>
  group_by(Question_Year) |>
  summarize(country_avg = mean(religion_avg, na.rm = TRUE))

religion_SHI_GRI <- religion_means |>
  ggplot(aes(x = Question_Year, y = country_avg)) +
  labs(title = "Religion Stigmatization Over Time", x = "Year", y = "Religious Stigma Average") +
  geom_point() +
  geom_smooth()

religion_SHI_GRI

fit <- lm(country_avg ~ Question_Year, data = religion_means)
fit


```
Religious Stigma Average (RSA) calculated from the average of government restrictions and social hostilities together, averaging all countries for each year.

## Analysis

Has religion become less stigmatized in the last two decades? Based on this data, as displayed in the graph, the answer is no. The visualization shows a low Religious Stigma Average (RSA) score across countries, starting at around 2.20 in 2007 and growing exponentially until 2012, reaching a high of just over 3.0. After that, the score dips dramatically to about 2.4 in 2014, and then follows with a small increase, decrease, and then plateau over the following 6 years, staying between 2.75 and 3.0.

There are a few reasons for the significant changes in religious stigma over this allotted time period. The initial, large but gradual increase in RSA is commonly associated with rising anti-Muslim sentiments, sectarian violence in Nigeria, and increased harassment regarding religious dress for women. The steep increase in 2012 is generally associated with the Arab Spring, occurring just before in 2010-2011. The relatively stabilized scores from 2016 on remain high, and typically connected with the decline of religious affiliation as a whole. Responding to the original question, beyond the smaller trends within, the graph shows an increase in RSA over time, as displayed by the mean line.
The regression shows a Question_Year value of about 0.03, which means for every one-year increase, the average Religious Stigma Average increases by 0.03. This is neither a huge or a catastrophic increase, but it is not negligible. This means within about 33 years, religious stigma average increases 10%.

With only short decreases, there is long-term exponential growth in religious stigma, showing that religious stigma has not decreased over time, rather it has grown.




